The Evolution of Manufacturing Ecosystem in Cloud Manufacturing Architecture

### 2016-06-26 head.tex
start the abstract structure
make up asap

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product. This shopping model makes it possible to centralised manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the servitization and optimization of manufacturing resource constitutes a central issue to  in such manufacturing ecosystem.

>>>>

\author[label1]{Author}
\address[label1]{ZJU}
\begin{abstract}
In Cloud Manufacturing, provider publish manufacturing resource as service on the platform for demander to search and purchase it as product. This shopping model makes it possible to centralized manage distributed massive manufacturing resources, which will potentially reduce the idle rate of those resources.
However, in the manufacturing ecosystem constructed with the platform, provider, demander and other components came along with, the heterogeneity of resource's attribute like type, quality, price, processing velocity, leads tough taxonomy of these resources, and the chaotic operating model makes it hard to meet demander's need.
Thus the way that each provider transforms his/her resource into product with servitization and optimization, constitutes a central issue in such manufacturing ecosystem, all these servitization and optimization activities brings the transition to the provider, and gradually, these individual transitions will brings the evolution to the ecosystem.

In this paper,
(study the resource servitization in the transitions way)
(propose a operation model for user to describe the transitions in the system) 
(in the god view as evolution to see the service pattern in a statistic view)
(simulate all this in an agent-bade method)
(evaluate which service pattern is effective for the resource user and environment friendly)
(make a proper explanation of all the emergency of the evolution)
